---
title: "Wine Quality Report"
author: "Omar Alshamrani"
output: html_document
date: '2022-06-16'
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# Libraries
library(tidyverse)
library(janitor)
library(here)
library(scales)
library(DT)
library(knitr)
library(reactable)
library(DataExplorer)
library(ggcorrplot)


# reading the dataset
wineRaw <- read.csv2(here('data/winequality-red.csv'))
```

## Introduction
Through this file, we will present a dataset on wine quality and we will investigate more about it.

## Variables Attributes

+--------------------+---------------+----------------------------------------------+
|Variable            |Type           |    Description                               |
+====================+===============+==============================================+
| fixed_acidity      |    Double     | most acids involved with wine or fixed or    |
|                    |               | nonvolatile (do not evaporate readily)       |
+--------------------+---------------+----------------------------------------------+
|Voltaile_acidity    |    Double     | the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
| citric_acid        |    Double     | found in small quantities, citric acid can add 'freshness' and flavor to wines|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|residual_sugar      |    Double     | the amount of sugar remaining after fermentation stops|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|chlorides           |    Double     | the amount of salt in the wine               |
+--------------------+---------------+----------------------------------------------+
|free_sulfur_dioxide |    Double     | the free form of SO2 exists in equilibrium between molecular SO2| 
|                    |               | (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|total_sulfur_dioxide|    Double     | amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm,| 
|                    |               | SO2 becomes evident in the nose and taste of wine|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|density             |    Double     | the density of water is close to that of water depending on the percent alcohol and sugar content|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|pH                  |    Double     | describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|sulphates           |    Double     | a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant|
|                    |               |                                              |
+--------------------+---------------+----------------------------------------------+
|alcohol             |    Double     | the percent alcohol content of the wine      |
+--------------------+---------------+----------------------------------------------+
|quality             |    Double     | Score between 3 and 8                        | 
+--------------------+---------------+----------------------------------------------+

## General information about the data

```{r , echo = FALSE}
reactable(wineRaw)
```

```{r}
summary(wineRaw)
```

## Interactive table 
```{r}
datatable(wineRaw)
```

## Plots
Now, note that some parts of the data are duplicated, but the duplications are removed before plotting the data.

```{r}
wine <- clean_names(wineRaw)
wine <- distinct(wine)

```


These are the distributions for each variable, where we can extract many information, such as skewness.

```{r}
wine %>% 
  DataExplorer::plot_density()
```

Also, This Correlogram shows how different factors are related.
The highest correlation with quality is alcohol.

```{r}
ggcorrplot(cor(wine), hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           colors = c("Cyan", "white", "Brown3"), 
           title="Correlogram of wine", 
           ggtheme=theme_bw)

```

## Conclusion

We used statistical methods using R script and we figured out that the more quality the wine has, almost the more people buy it, and the most correlated feature to the quality is the amount of alcohol.


